---
title: "Final Workflow Report"
author: "Deja Simon"
output: html_document
---

## *Organization*

The initial changes I made pertained to my workflow's organization. 

### Change #1: Project Creation

I first created a project to house my data files and analysis script. I set this up to improve the sharability and reproducibility of my workflow, so that the raw data would not just live on my computer. Now, someone interested in looking over and/or reproducing my analysis will have access to the data as well.  

I would previously load in the data from my working directory:  
```{r eval=FALSE}
setwd("~/Desktop/RSSC/GIRA/Raw Data")

data <- read.csv("GIRA2_raw.csv")
```

Now, I use the `here` function to load the data from the "data_raw" folder within the project:  
```{r eval=FALSE}
data <- read_csv(here("data_raw", "GIRA2_raw.csv"))
```

### Change #2: File Separation

The original version consisted of one large RMarkdown file, which was long and tedious to navigate (I like to use Markdown rather than regular script files beause I can separate each step into labeled chunks). While not mentioned in my critique assignment, I decided to make this change because I was tired of dealing with one long file; also, hearing my classmates' and instructors' takes on the utility of making separate scripts solidified that this would be a useful adjustment.  
  
I accomplished this by manually breaking up the file into multiple Markdown scripts (e.g., “Data Import and Cleaning”, “Data Transformation”, “Data Analysis”). The files can be seen in my GitHub repository.  

## *Repetition Reduction*

The remainder of my changes involved decreasing repetitive code. Repetition (i.e., a lot of copy and paste) occurred in multiple sections of the workflow, so I felt it was important to devote the bulk of my changes to these areas. Executing these adjustments was challenging for me, but in the end I was able to successfully reduce repetition in several spots.

### Change #3: Functions

The primary way I reduced repetition was by creating functions. 

The first two functions I created were for the Social Dominance Orientation scale items. I initially had the same lines of code for each item: 
```{r eval=FALSE}
# recoding reverse items
data$SDO1 <- revalue(data$SDO1, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO2 <- revalue(data$SDO2, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO3 <- revalue(data$SDO3, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO4 <- revalue(data$SDO4, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO5 <- revalue(data$SDO5, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO6 <- revalue(data$SDO6, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO7 <- revalue(data$SDO7, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))
data$SDO8 <- revalue(data$SDO8, c("7"="1", "6"="2", "5"="3", "4"="4", "3"="5", "2"="6", "1"="7"))


# making all the items numeric
data$SDO1 <- as.numeric(as.character(data$SDO1))
data$SDO2 <- as.numeric(as.character(data$SDO2)) 
data$SDO3 <- as.numeric(as.character(data$SDO3)) 
data$SDO4 <- as.numeric(as.character(data$SDO4)) 
data$SDO5 <- as.numeric(as.character(data$SDO5))
data$SDO6 <- as.numeric(as.character(data$SDO6))
data$SDO7 <- as.numeric(as.character(data$SDO7))
data$SDO8 <- as.numeric(as.character(data$SDO8))
data$SDO9 <- as.numeric(as.character(data$SDO9))
data$SDO10 <- as.numeric(as.character(data$SDO10))
data$SDO11 <- as.numeric(as.character(data$SDO11))
data$SDO12 <- as.numeric(as.character(data$SDO12))
data$SDO13 <- as.numeric(as.character(data$SDO13))
data$SDO14 <- as.numeric(as.character(data$SDO14))
data$SDO15 <- as.numeric(as.character(data$SDO15))
data$SDO16 <- as.numeric(as.character(data$SDO16))
```

Using custom functions and automation (the `across` function, specifically), I was able to eliminate this repetitive copy and pasting:

```{r eval=FALSE}
reverseCode <- function(var) {
 var <- recode(var, `7`= 1, `6` = 2, `5` = 3, `4` = 4, `3` = 5, `2` = 6, `1` = 7)
}
data <- data %>% mutate(across(SDO1:SDO8, reverseCode))


asNumeric <- function(var) {
 var <- as.numeric(as.character(var))
}
data <- data %>% mutate(across(SDO1:SDO16, asNumeric))
```

One area where there was significant copy and pasting was within data transformation. The purpose of this code was to count the number of hits, correct rejections, false alarms, and misses for stimuli of three different ethnicities: 
```{r eval=FALSE}
# White stimuli
num_of_hits_white <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(hits_white = case_when(Correct == '1' & Type == "White" ~ 1, TRUE ~ 0)) %>% tally(hits_white)

num_of_cr_white <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(cr_white = case_when(Correct == '2' & Type == "White" ~ 1, TRUE ~ 0)) %>% tally(cr_white)

num_of_fa_white <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(fa_white = case_when(Incorrect == '1' & Type == "White" ~ 1, TRUE ~ 0)) %>% tally(fa_white)

num_of_miss_white <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(miss_white = case_when(Incorrect == '2' & Type == "White" ~ 1, TRUE ~ 0)) %>% tally(miss_white)


# Black stimuli
num_of_hits_black <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(hits_black = case_when(Correct == '1' & Type == "Black" ~ 1, TRUE ~ 0)) %>% tally(hits_black)

num_of_cr_black <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(cr_black = case_when(Correct == '2' & Type == "Black" ~ 1, TRUE ~ 0)) %>% tally(cr_black)

num_of_fa_black <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(fa_black = case_when(Incorrect == '1' & Type == "Black" ~ 1, TRUE ~ 0)) %>% tally(fa_black)

num_of_miss_black <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(miss_black = case_when(Incorrect == '2' & Type == "Black" ~ 1, TRUE ~ 0)) %>% tally(miss_black)


# Latinx stimuli
num_of_hits_latinx <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(hits_latinx = case_when(Correct == '1' & Type == "Latinx" ~ 1, TRUE ~ 0)) %>% tally(hits_latinx)

num_of_cr_latinx <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(cr_latinx = case_when(Correct == '2' & Type == "Latinx" ~ 1, TRUE ~ 0)) %>% tally(cr_latinx)

num_of_fa_latinx <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(fa_latinx = case_when(Incorrect == '1' & Type == "Latinx" ~ 1, TRUE ~ 0)) %>% tally(fa_latinx)

num_of_miss_latinx <- fem.cfBasic %>% group_by(ResponseId) %>% mutate(miss_latinx = case_when(Incorrect == '2' & Type == "Latinx" ~ 1, TRUE ~ 0)) %>% tally(miss_latinx)
```

To improve this code, John and Jake helped me create a function that could be applied to each ethnicity:
```{r eval=FALSE}
sigDet <- function(data, type) {
num_of_hits <- data %>% group_by(ResponseId) %>% mutate(hits = case_when(Correct == '1' & Type == type ~ 1, TRUE ~ 0)) %>% tally(hits) 

num_of_cr <- data %>% group_by(ResponseId) %>% mutate(cr = case_when(Correct == '2' & Type == type ~ 1, TRUE ~ 0)) %>% tally(cr)

num_of_fa <- data %>% group_by(ResponseId) %>% mutate(fa = case_when(Incorrect == '1' & Type == type ~ 1, TRUE ~ 0)) %>% tally(fa) 

num_of_miss <- data %>% group_by(ResponseId) %>% mutate(miss = case_when(Incorrect == '2' & Type == type ~ 1, TRUE ~ 0)) %>% tally(miss) 

cbind(num_of_hits, num_of_cr$n, num_of_fa$n, num_of_miss$n) %>% set_names("ResponseId", paste0(type,"_hits"), paste0(type,"_crs"), paste0(type,"_fas"), paste0(type,"_misses"))
}
```

Finally, I computed various t-tests and effect sizes within my data analysis. These are a couple of examples:
```{r eval=FALSE}
# White vs. Black d'
t.test(cf$whiteD,
       cf$blackD,
       paired=TRUE,
       conf.level=0.95)

cohen.d(cf$whiteD,
        cf$blackD,
        paired=TRUE,
        conf.level=0.95)

# White vs. Black c
t.test(cf$whiteC,
       cf$blackC,
       paired=TRUE,
       conf.level=0.95)

cohen.d(cf$whiteC,
        cf$blackC,
        paired=TRUE,
        conf.level=0.95)
```

By creating t-test and Cohen's D functions, I was able to run these analyses without copy and pasting the code each time: 
```{r eval=FALSE}
# White vs. Black d'
tTest(whiteD, blackD)
cohenD(whiteD, blackD)

# White vs. Black c
tTest(whiteC, blackC)
cohenD(whiteC, blackC)
```

--  

In conclusion, while my new workflow isn't perfect, I was able to increase its efficiency, fidelity, and sharing/reproducibility in multiple ways. 